---
title: "Two column test"
# author: "Grant McDermott"
# date: "6/28/2019"
output:
  html_document:
    css: preamble.css
  pdf_document:
    includes:
      in_header: preamble.tex
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

This is an example R Markdown script that allows for two column (side-by-side) code and text environments knitted to both PDF and HTML output. It is based on [Section 4.8](https://bookdown.org/yihui/rmarkdown-cookbook/multi-column-layout.html) of the [*R Markdown Cookbook*](https://bookdown.org/yihui/rmarkdown-cookbook/) (Xie & Dervieux). The **tl;dr** version is that we use Pandoc's [fenced divs](https://pandoc.org/MANUAL.html#extension-fenced_divs) syntax (`:::`), having specified the necessary environments for each output type in the associated .css and .tex preamble files that we include in the YAML.


To illustrate, here comes a section in two columns.

:::::: {.columns}
::: {.column width="48%" data-latex="{0.48\textwidth}"}
### Python

```{python, eval=FALSE}
## This is where your Python code would go.
```
:::
::: {.column width="4%" data-latex="{0.04\textwidth}"}
\ 
<!-- an empty Div (with a white space), serving as
a column separator -->
:::
:::::: {.column width="48%" data-latex="{0.48\textwidth}"}
### R

```{r, eval=FALSE}
## And this is where your R code would go.
```
:::
::::::
\newline

And then we could continue writing. We could still use regular code chunks spanning the whole page if we wanted.

```{r p}
library(ggplot2)
set.seed(1234)

p = 
  ggplot(
  data.frame(x= rnorm(1e4), y = rnorm(1e4)), 
  aes(x = x, y = y)
  ) +
  geom_hex() + 
  coord_fixed() +
  theme_void()
```

And then revert back to the side-by-side format when needed.

:::: {.columns}

::: {.column width="48%" data-latex="{0.48\textwidth}"}
### Some people like viridis default
```{r viridis_default, dependson=p}
p + scale_fill_viridis_c()
```
:::

::: {.column width="4%" data-latex="{0.04\textwidth}"}
\ 
<!-- an empty Div (with a white space), serving as
a column separator -->
:::

::: {.column width="48%" data-latex="{0.48\textwidth}"}
### Others prefer viridis magma
```{r viridis_magma, dependson=p}
p + scale_fill_viridis_c(option="A")
```
:::

::::
\newline