---
title: "Two column test"
# author: "Grant McDermott"
# date: "6/28/2019"
output:
  pdf_document:
    includes:
      in_header: preamble.tex
  html_document:
    css: preamble.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = T)
library(tidyverse)
set.seed(1234)
```

This is an example Rmarkdown script that allows for two column (side-by-side) code environments knitted to both PDF and HTML output. The key is to include two preamble files --- `preamble.tex` for PDF and `preamble.css` for HTML --- in the YAML. You can then mix LaTeX and HTML code within the same document, and the knitr engine will safely ignore any commands that aren't relevant to that output format. For example, it will ignore any HTML `<div>` tags when knitting to PDF. 

To illustrate, here comes some code in two columns.

<div class="column-left">
\twocol
#### Stata
```{stata, eval=F}
## This where your Stata code would go.
```
</div>
\columnbreak
<div class="column-right">
#### R
```{r, eval=F}
## And this is where your R code would go.
```
\etwocol
</div>

And then we could continue writing. And now come some figures, because who doesn't want to see more figures?

<div class="column-left">
\twocol
#### Some people like viridis default
```{r}
ggplot(
  data.frame(x= rnorm(1e4), y = rnorm(1e4)), 
  aes(x = x, y = y)
  ) +
  geom_hex() + coord_fixed() +
  scale_fill_viridis_c() + 
  theme_void()
```
</div>
\columnbreak
<div class="column-right">
#### Others prefer viridis magma
```{r}
ggplot(
  data.frame(x= rnorm(1e4), y = rnorm(1e4)), 
  aes(x = x, y = y)
  ) +
  geom_hex() + coord_fixed() +
  scale_fill_viridis_c(option="A") + 
  theme_void()
```
\etwocol
</div>

And then you would continue writing here...